%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {AxioCode - Web and Mobile development} % Organization
    {Metz, France - On site} % Location
    {02/2024 - Present} % Date(s)
    {
        I contribute to the development and maintain a web application and API for athlete management and competition organization in the field of equestrianism.
        \newline
        \textbf{Skills}: PHP, .Net Framework, .Net Core, ASP.Net, MSSQL Server, PostgreSQL, Docker, Linux, Windows, Web Application Design, Angular, AWS, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {IT Developer} % Job title
    {GVA Africa - FTTH Deployment in Central Africa} % Organization
    {Paris, France - Full remote} % Location
    {08/2023 - 02/2024} % Date(s)
    {
        I contribute to the development and maintenance of an API to manage the configuration and deployment of internet boxes. 
        \newline
        I manage the evaluation of new hardware to assess its compatibility with our existing system. 
        \newline
        In addition, I implement and/or update features to integrate this new hardware.
        \newline
        \textbf{Skills}: Python, API development, Fiber Optic Networks, OLT, Git, CI/CD, Ansible.
    }

%---------------------------------------------------------
  \cventry
    {Fullstack developer} % Job title
    {LiNote - Elderly people help} % Organization
    {Nancy, France - Full remote} % Location
    {01/2023 - 07/2023} % Date(s)
    {
        I contribute to the development and maintenance of an API for managing communication assistance systems for the elderly or disabled.
        \newline
        \textbf{Skills}: Docker, Django, Django REST Framework, Flask, Peewee, Python, PostgreSQL, AWS, Angular, Android, Salt, Zabbix, Twillio, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {IT Project Manager} % Job title
    {Crédit Agricole de Lorraine - Bank \& Insurance} % Organization
    {Metz, France - On site} % Location
    {02/2022 - 12/2022} % Date(s)
    {
        Within the "Péri-Informatique" team, I am the local referent of a project which aims to
        update the development stack used during development of private applications for the
        regional business unit.
        \newline
        This project will lead to the establishment of a CI/CD chain, the management of a 
        registry, and the use of a kubernetes scheduler.
        \newline
        In addition to this role, I work on the development of business applications based 
        on the current development stack.
        \newline
        \textbf{Skills}: PHP, jQuery, MSSQL Server, React, NodeJs, Kubernetes, Docker, Registry, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Quality and Methods Engineer - DeveOps Engineer} % Job title
    {AxioCode - Web and Mobile development} % Organization
    {Metz, France - On site} % Location
    {02/2020 - 02/2022} % Date(s)
    {
        Within this Web solution editor, I joined the team responsible for improving processes and quality within the company.
        \newline
        \textbf{Skills}: Google Suite, Development PHP, Python, Typescript, Javascript, VisualParadigm, Docker, Docker-Swarm, Kubernetes, Harbor, Traefik, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Senior Developer - Lead Tech Developer} % Job title
    {ProConsultant Informatique - TV-Media solution editor} % Organization
    {Metz, France - On site} % Location
    {03/2019 - 02/2020} % Date(s)
    {
        Within a leader in the development and implementation of enterprise management software for the media industry. I joined the solution development team.
        \newline
        \textbf{Skills}: Development SQL, Java / SpringBoot, C++ / Boost, Python / PyUnit, Flask and Django, PHP / Laravel, PHPUnit, Typescript / React.js, C\#.Net, PL/SQL, Git, CI/CD, Multiple Operating Systems Servers management (Windows Server), Linux (Debian, RedHat).
    }

%---------------------------------------------------------
  \cventry
    {Technical Referent (French business portage)} % Job title
    {Raiffeisen Bank via Lux Pro Consulting - Bank} % Organization
    {Leudelange, Luxembourg - On site} % Location
    {12/2018 - 03/2019} % Date(s)
    {
        I joined the Business Application Development team of Raiffeisen Community Bank 
        as a Web Development Referent to manage requierement of frontend developements 
        and to be the point of contact with external providers.
        \newline
        \textbf{Skills}: Typescript and Angular 7 developement, Git, CI/CD, OpenStack.
    }

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {BizzDev - ESN} % Organization
    {Luxembourg, Luxembourg - Hybrid} % Location
    {10/2017 - 12/2018} % Date(s)
    {
        I work on various client projects using various technologies.
        \newline
        \textbf{Skills}: Azure, C\# .Net Core, Angular, ReactJs, Redux, RxJs, MSSQL Administration,
        Automation AnyWhere (RPA), Python, Odoo, Git, TFS, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Fullstack developer} % Job title
    {Sogeti - ESN} % Organization
    {Bertrange, Luxembourg - On site} % Location
    {05/2017 - 10/2017} % Date(s)
    {
        For a major world retailer, I joined the team responsible for creating a 
        Web and Mobile application allowing the site and department manager to manage 
        their stock and get sales statistics feedback to help them with the shelving 
        of their sector.
        \newline
        \textbf{Skills}: Angular, JavaEE, Spring, Hibernate, PostgreSQL, Git, CI/CD,
        Maven, Jenkins, SonarQube, Private Docker Registry.
    }

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {Abylsen Est - ESN} % Organization
    {Metz, France - On site} % Location
    {01/2016 - 05/2017} % Date(s)
    {
        On assignment in the IT management center of a major retailer in France, 
        I joined the team in charge of the Drive part. 
        \newline
        I participated in the maintenance and evolution of the current Drive platform. 
        \newline
        I participated in the development of the Drive API initially created as part 
        of a project for Mobile Application of the Drive and which will then be used 
        by the Web platform.
        \newline
        \textbf{Skills}: PHP (5.x / 7.x), Lumen/Laravel/Passport, Perl, Template Toolkit, Typo3,
        jQuery, Bootstrap, HTML5 / CSS3, MySQL, Subversion.
    }

%---------------------------------------------------------
  \cventry
    {Embedded Systems developer} % Job title
    {Moneo / Applicam (Docapost) - Solutions editor} % Organization
    {Metz, France - On site} % Location
    {02/2014 - 02/2016} % Date(s)
    {
        Internally at a publisher of solutions based on smart card management systems, 
        I maintained and developed one of their key solutions for the management of 
        fuel cards used by customers such as TOTAL (AMO).
        \newline
        I oversaw needs analysis, writing functional specifications with the client's 
        business team, writing end-of-sprint recipe books, writing technical specifications 
        for the development team. 
        \newline
        I was also responsible for writing user documents (French/English)
        \newline
        \textbf{Skills}: C/C++; Bank payment terminals, Security, Python, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Analyst developer} % Job title
    {EBM Consulting - SAP ESN} % Organization
    {Basacharage, Luxembourg - Flex Hybrid} % Location
    {10/2012 - 02/2014} % Date(s)
    {
        Internally in an ESN whose core business is based on SAP technologies, I oversaw the correction 
        and evolution of an employment platform (the company wanted to diversify its activity and have 
        a canvassing tool for freelancers and end customers).
        \newline
        \textbf{Skills}: MySQL, PHP /Zend Framework, Joomla, Telephony Appliance Management,
        CRM VTiger, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Open-source Consultant} % Job title
    {ArcelorMittal HQ Europe - Steel Manufacturer} % Organization
    {Luxembourg, Luxembourg - On site} % Location
    {07/2006 - 10/2012} % Date(s)
    {
        Within the Open Source then IAM team, I contributed to the realization of various projects as a technical referent.
        Projects like official web site, SSO, IAM, and so on, and so on
        \newline
        \textbf{Skills}: MySQL, MSSQL, PHP, Python, Perl, System and Network, Mail routing
        IAM, SSO, VoIP, Apache, IIS, Git, CI/CD.
    }

%---------------------------------------------------------
  \cventry
    {Engineer} % Job title
    {ALTEN Tehcno Est - ESN} % Organization
    {Starsbourg, France - On site} % Location
    {03/2006 - 07/2006} % Date(s)
    {
        As a VoIP consultant, I implemented the client's internal IP telephony system 
        as well as the implementation of a Call-Center. The chosen solution was an 
        Open-Source solution (Asterisk). 
        \newline
        I also carried out training and user support.
        \newline
        \textbf{Skills}: MySQL, CISCO Network, VoIP, PHP, Perl, Python, Git.
    }

%---------------------------------------------------------
  \cventry
    {Engineer \& Project Manager} % Job title
    {University of Lorraine} % Organization
    {Metz, France - On site} % Location
    {11/2004 - 03/2006} % Date(s)
    {
        As Wi-Fi Network Project Manager, I was able to carry out the project to set up a 
        Wi-Fi network at the University of Metz (Multi-sites geographical). 
        \newline
        From the needs analysis to the delivery of the system, I wrote all the documents 
        necessary for the project (Needs analysis, Functional Specifications, Technical 
        Specifications, Call for Tender, Choice of supplier, Deployment schedule) 
        \newline
        I also carried out training and user support.
        \newline
        \textbf{Skills}: MySQL, Oracle, PHP, Python, C\#.Net (Mono), Perl, CISCO Network,
        VoIP, Subversion, Git.
    }

\end{cventries}